Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
Remove ta as argument of code region.
Use a macro where useful.

We define a component as follows:
\begin{align*}
  \var{comp} &\mathrel{::=} (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c}_{\mathrm{import}},\overline{c}_{\mathrm{export}},\sigrets,\sigcloss)
\end{align*}

@@

\[
  \codereg{\ta,\sigrets,\sigcloss,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigrets \; \sigcloss \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigrets \; \sigcloss \; \code)
\]

\begin{equation*}
  H^\mathrm{code} \; \ta \; \sigrets \; \sigcloss \; \code \; s \; \hat{W} = \left\{\npair{(\code,\code)} \middle|
    \dom(\code) = [\aaddr,\baddr]
  \right\}
\end{equation*}

\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigrets \; \sigcloss \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \lbrack \baddr, \eaddr \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma \in \sigcloss \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{(\vsc,\vsc')} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta \tand \npair{(\vsc,\vsc')} \in \lrvtrusted \; W)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}

@@

\dominique{19-3-2018: components should contain information about what seals they use and for what (for building return pointers or for building closures). That should facilitate defining reasonable linking (only when seals disjoint), and for defining the condition for full abstraction and the FTLR.}
\begin{definition}
  A component $\program = (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)$ with $\dom(\ms_{\mathrm{code}}) = \ta$, is reasonable if for all $n$ and all contexts $\context$ the configuration $\plug{\context}{\program}$ satisfies:
  \begin{itemize}
  \item $\plug{\context}{\program}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
  \item $\plug{\context}{\program}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
  \item $\plug{\context}{\program}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
  \item $\plug{\context}{\program}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
  \end{itemize}
\end{definition}

>>>>

We define a component as follows:
\begin{align*}
  \var{comp} &\mathrel{::=} (\mscode,\msdata,\overline{c}_{\mathrm{import}},\overline{c}_{\mathrm{export}},\sigrets,\sigcloss)
\end{align*}

@@

\[
  \codereg{\sigrets,\sigcloss,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \sigrets \; \sigcloss \; \code,H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \code)
\]

\begin{equation*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; s \; \hat{W} = \left\{\npair{(\code,\code)} \middle|
    \dom(\code) = [\aaddr,\baddr]
  \right\}
\end{equation*}

\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \lbrack \baddr, \eaddr \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma \in \sigcloss \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{(\vsc,\vsc')} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta \tand \npair{(\vsc,\vsc')} \in \lrvtrusted \; W)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}

@@

\dominique{19-3-2018: components should contain information about what seals they use and for what (for building return pointers or for building closures). That should facilitate defining reasonable linking (only when seals disjoint), and for defining the condition for full abstraction and the FTLR.}
\begin{definition}
  A component $\program = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)$ with $\dom(\mscode) = \ta$, is reasonable if for all $n$ and all contexts $\context$ the configuration $\plug{\context}{\program}$ satisfies:
  \begin{itemize}
  \item $\plug{\context}{\program}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
  \item $\plug{\context}{\program}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
  \item $\plug{\context}{\program}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
  \item $\plug{\context}{\program}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
  \end{itemize}
\end{definition}
